\LARGE \bf {\sc underworlds}: Cascading Situation Assessment for Robots

### 2017-02-28 paper.tex
Cleared other comments from Chris
Added 'underworlds' to title, as per James suggestion
Future work section

\title{\LARGE \bf
Cascading Situation Assessment for Robots
}

@@

%CDW - Remove 'Besides'. I think you are trying to establish why uwds is not like previous work but I don't think that word quite works in there. Probably ok with just removing it.
Work on distributed scene graphs~\cite{naef2003blue} has been previously applied
to robotics to provide a shared 3D representation of the robot's environment
(for instance, the \emph{Robot Scene Graph}~\cite{blumenthal2013scene} or the
\emph{Deep State Representation} proposed in~\cite{bustos2016unified}).  \uwds
offers a similar distribution mechanism for 3D scene graphs and extends it to
temporal representations. Besides, \uwds further extends this line of work by
providing the ability to create, manipulate and share \emph{multiple alternative
worlds}. As an example, these could correspond to filtered or hypothetical \emph{views} on
the initial, perceived model of the environment.

@@

% JK: like software, the plural of middleware is middleware :)
% CDW: I get the analogy with first-class citizens but perhaps better to replace with something like 'but is not a great strength' or 'but is not a highly developed feature'
Traditional robotic middleware, like ROS, is not particularly well-suited to
deal with these different needs: full geometric data can be represented, but are
not first-class citizens (a basic task like displaying a 3D mesh at a dynamic
position is not particularly easy to perform with ROS) and critically,
representing and reasoning on alternative states of the environment is not
directly feasible.

@@

\section{Application Example}

@@

Representation of uncertainty

Representation of fields

Client libraries in more languages

@@

We have introduced \uwds, a novel framework for shared and composable
spatio-temporal representations of a robot's world. The key contributions of our
approach are: a composite data-structure for environment representation within a
robotic software architecture, made of a scene graph and a timeline; a mechanism
to efficiently and transparently share this data-structure amongst a set of
clients (the software modules of the robot); a cascading architecture permitting
the explicit of representation of alternative states of the world while
maintaining a network of dependencies amongst themselves; a typology of clients
(\emph{root}, \emph{leaf}, \emph{filter}, \emph{transformer}) to systematically
describe such a network of representations dependencies.

>>>>

\title{\LARGE \bf
{\sc underworlds}: Cascading Situation Assessment for Robots
}

@@

Work on distributed scene graphs~\cite{naef2003blue} has been previously applied
to robotics to provide a shared 3D representation of the robot's environment
(for instance, the \emph{Robot Scene Graph}~\cite{blumenthal2013scene} or the
\emph{Deep State Representation} proposed in~\cite{bustos2016unified}).  \uwds
offers a similar distribution mechanism for 3D scene graphs and extends it to
temporal representations. Besides, \uwds further extends this line of work by
providing the ability to create, manipulate and share \emph{multiple alternative
worlds}. As an example, these could correspond to filtered or hypothetical \emph{views} on
the initial, perceived model of the environment.

@@

Traditional robotic middleware, like ROS, is not particularly well-suited to
deal with these different needs: full geometric data can be represented, but are
not first-class citizens (a basic task like displaying a 3D mesh at a dynamic
position is not particularly easy to perform with ROS) and critically,
representing and reasoning on alternative states of the environment is not
directly feasible.

@@

\section{Application Example}
\label{application}

@@

As illustrated in section~\ref{application}, \uwds is already deployed and used
on the field. Several features are however still under development.

\subsubsection{Representation capabilities} as presented in
section~\ref{design}, the current version of \uwds allows to represent
\emph{objects}, \emph{abstract entities} like groups and \emph{perspectives}.
\emph{Fields} are also part of the \uwds design, but are not yet implemented.

\paragraph*{Representation of fields} fields are commonly used to represent
continuously-valued spatial entities. Fields might or might not be spatially
bounded. Examples include the working space of a robot arm (spatially bounded),
the field of view of a camera (spatially bounded), proxemics (potentially
unbounded). We plan to represent fields in \uwds using the memory-efficient
octomaps~\cite{hornung2013octomap}. Similarly to geometric data, octomaps
will not be directly stored with the nodes (nodes will refer to them through 
handles), but unlike geometric data, they will not be treated as immutable
datasets by the server, permitting real-time updates.

\paragraph*{Representation of uncertainty} currently node positions are 
stored as $4\times4$ transformation matrices, relative to the node parent. This
representation is efficient, and conveniently matches traditional representation
systems (including ROS TF frames or OpenGL transformations). However, the explicit management
of uncertainties is instrumental to many robotic applications, and we plan to
add full support for position uncertainties to \uwds. We plan to add this
support by adding a pose covariance matrix to the nodes, and equipping the
different \uwds helper tools with corresponding support (like covariance
ellipses visualisation in {\tt uwds view}).

\subsubsection{Manipulation of representations} \uwds makes it possible to
cheaply clone and modify multiple worlds. However, little is provided to
jointly manipulate sets of worlds. In that regard, we plan to add a mechanism to
efficiently \emph{compare} two worlds. This would permit a client
to quickly identify modifications applied to a world, and could prove especially
useful when combined with temporal events to answer questions like ``what has
changed in the scene?''. Comparisons between worlds involves the definition of
an efficient fuzzy \emph{diff} algorithm for 3D scene graphs, able to
selectively ignore non-relevant micro displacements.

\subsubsection{Implementation and Integration} finally, we plan to continue to
improve the integration of \uwds into existing software architectures. A
short-term goal is to provide excellent C++ support, with a high-level,
user-friendly C++ client library. This is critical for a broader adoption of \uwds
within the robot community. Support for other languages might follow, depending
on demands and open-source contributions.

In term of implementation, we are also investigating alternative back-ends that
could compete with gRPC to provide the synchronisation mechanisms between
clients. Due to the high-level nature of \uwds (a set of shared, tree-like data
structures), the use of the GIT version control system is one particular (if
unusual) option being studied. The scene graph would be represented as a
hierarchy of directories, nodes would be files in these directories, creating
new worlds would consist in creating a branch in the repository, and sharing
would be supported through the usual pull/push GIT mechanisms. Initial
prototyping shows that under the right conditions (in particular, an in-memory
file system), performance is not an issue. Automatic conflicts resolution, on
the other hand, might prove more challenging.

@@

We have introduced \uwds, a novel framework for shared and composable
spatio-temporal representations of a robot's world. The key contributions of our
approach are: a composite data structure for environment representation within a
robotic software architecture, made of a scene graph and a timeline; a mechanism
to efficiently and transparently share this data structure amongst a set of
clients (the software modules of the robot); a cascading architecture permitting
the explicit of representation of alternative states of the world while
maintaining a network of dependencies; a typology of clients
(\emph{root}, \emph{leaf}, \emph{filter}, \emph{transformer}) to systematically
describe such a network of representations dependencies.
